Computable Poincar\'e--Friedrichs constants\\ for the $L^{p}$ de Rham complex over domains\\ with shellable triangulations

### 2024-08-15 draft.tex
transformation

    Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. However, no operator norm estimates are given in the literature, to the best of our best knowledge.
    We study a variation of this potential operator over convex sets.
    We simply use a constant averaging over the entire domain. 
    While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
    this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms. 
\end{document}

@@

>>>>

    Their analysis identifies the potential as a pseudodifferential operator of negative order and utilizes tools of harmonic analysis. However, no operator norm estimates are given in the literature, to the best of our best knowledge.
    We study a variation of this potential operator over convex sets.
    We simply use a constant averaging over the entire domain. 
    While the resulting Bogovski\u{\i}-type potential has more moderate regularity properties, 
    this simplification suits our purposes and enables some simple estimates for the continuity constant of the potential operator in Lebesgue norms.

@@

On the other hand, by the reverse triangle inequality,
    \begin{align}
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{y}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right\|
        \\&
        \geq 
        \left| 
            \frac{\|x\|}{\|x\|}
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \frac{\|y\|}{\|y\|}
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \sum_{i=1}^{n} \lambda_{i}(x)
            -
            \sum_{i=1}^{n} \lambda_{i}(y)
        \right|
        \\&
        = 
        \left| 
            \vec{1}
            \cdot 
            A^{-1}( x - y )
        \right|
    \end{align}
    Note that $A^{-1}( x - y ) \in \Delta^{n} - \Delta^{n}$. 
    \begin{align}
        \left| F(x) - F(y) \right|
        &\geq 
        \left\| 
            \frac{x}{\|x\|}
            \left( 1 - \lambda_{0}(x) \right) 
            -
            \frac{y}{\|y\|}
            \left( 1 - \lambda_{0}(y) \right) 
        \right\|
        \\&
        \geq 
        \left\| 
            \frac{x}{\|x\|}
            \left( 1 - \lambda_{0}(x) \right) 
            -
            \frac{y}{\|y\|}
            \left( 1 - \lambda_{0}(y) \right) 
        \right\|
    \end{align}
    %% \todo{finish this estimate somehow}

    \begin{proof}
\begin{itemize}
    \item 
    % \todo{Choose hyperplane that puts T on one side}
    We use Lemma~\ref{lemma:oppositesubsimplex}
    \item 
    % \todo{Align barycenter of opposite subsimplex with coordinate axis}
    \item 
    % \todo{opposite simplex cast to disk}
    \item 
    % \todo{roll out rest of sphere onto disk}
    \item 
    % \todo{estimate reflection}
\end{itemize}
\end{proof}

    We use the following auxiliary result. 
    Suppose that $\|\cdot\|_{\alpha}$ and $\|\cdot\|_{\alpha}$ are two norms on a Banach space.
    Let 
    $$
        F_{\alpha,\beta}(x) = \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} }.
    $$
    Then 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        C_{\beta}^{\alpha} 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \left\| 
            \| y \|_{\alpha} \frac{ x }{ \| y \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left| 
            \| x \|_{\alpha}
            \| y \|_{\alpha}
        \right|
        C_{\beta}^{\alpha} 
        \frac{ \| y \|_{\alpha} }{ \| y \|_{\beta} } 
        \left\| x - y \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        C_{\alpha}^{\beta} 
        \left\| x - y \right\|_{\alpha}
        C_{\beta}^{\alpha} 
        C_{\alpha}^{\beta} 
        \left\| x - y \right\|_{\alpha}
        \| 
            F(x) - F(y) 
        \|_{\beta}
        \\&\leq 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \\&\leq 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \\&\leq 
        \left\| 
            \| x \|_{\alpha} \frac{ x }{ \| x \|_{\beta} } 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| x \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
        \right\|_{\beta}
        \left\| 
            \| y \|_{\alpha} \frac{ y }{ \| x \|_{\beta} } 
            \| y \|_{\alpha} \frac{ y }{ \| y \|_{\beta} } 
        \right\|_{\beta}
        \\&\leq 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        \frac{ \| y \|_{\beta} }{ \| x \|_{\beta} } 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
        \left| 
            \frac{ 1 }{ \| x \|_{\beta} } 
            \frac{ 1 }{ \| y \|_{\beta} }  
        \right|
        \\&\leq 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        % BEcause w l o g 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
        \\&\leq 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| 
            x - y
        \right\|_{\beta}
        % BEcause w l o g 
        \left| \| x \|_{\alpha} - \| y \|_{\alpha} \right|
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left| \| x \|_{\beta} - \| y \|_{\beta} \right| }{ \| x \|_{\beta} \| y \|_{\beta} }
        \\&\leq 
        \frac{ \| x \|_{\alpha} }{ \| x \|_{\beta} } 
        \left\| x - y \right\|_{\beta}
        % BEcause w l o g 
        \left\| x - y \right\|_{\alpha}
        \| y \|_{\alpha} \| y \|_{\beta} 
        \frac{ \left\| x - y \right\|_{\beta} }{ \| y \|_{\beta} \| y \|_{\beta} }
        \\&\leq 
        C^{\alpha}_{\beta} 
        C^{\beta}_{\alpha}
        \left\| x - y \right\|_{\alpha}
        % BEcause w l o g 
        \left\| x - y \right\|_{\alpha}
        C^{\alpha}_{\beta} 
        C^{\beta}_{\alpha}
        \left\| x - y \right\|_{\alpha}
    % \item 
    Consider any simplex $T$ with one vertex $v_0$ at the origin. 
    Let $\lambda_{0}, \lambda_{1}, \dots, \lambda_{n}$ be the barycentric coordinates. 
    The mapping 
    \begin{align}
        F(x) = \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right) = \frac{x}{\|x\|} \left( 1 - \lambda_{0}(x) \right)
    \end{align}
    maps $T$ onto a ``simplex with a curved face'' inside the unit ball. We analyze its Lipschitz properties.
    On the one hand, 
    \begin{align}
        F(x) - F(y)
        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{y}{\|x\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{y}{\|y\|} \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
    \end{align}
    Without loss of generality, $\|y\| \leq \|x\|$. 
    \begin{align}
        \left\| F(x) - F(y) \right\|
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
        \\&\leq
        \left\| x - y \right\|
        \sqrt{n} \sigma_{\min}(A^{-1})
        \sqrt{n} \sigma_{\min}(A^{-1}) \left\| x - y \right\|
        \left\| x - y \right\|
        \sqrt{n} \sigma_{\min}(A^{-1})
        \\&\leq
        3\sqrt{n} \sigma_{\min}(A^{-1})
        \left\| x - y \right\|
    \end{align}
    \begin{align}
        \left\| F(x) - F(y) \right\|
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \sum_{i=1}^{n} \lambda_{i}(x) - \sum_{i=1}^{n} \lambda_{i}(y) \right|
        \|y\| \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\| \|y\|}
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \left| \|y\| - \|x\| \right| }{\|x\|}
        \\&\leq
        \left\| x - y \right\|
        \frac{\sum_{i=1}^{n} \lambda_{i}(x)}{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \sum_{i=1}^{n} \lambda_{i}(y) \right)
        \frac{ \| x - y \| }{\|x\|}
        \\&\leq
        \left\| x - y \right\|
        \frac{ \lambda_{0}(x) }{\|x\|}
        \left| \lambda_{0}(x) - \lambda_{0}(y) \right|
        \left( \lambda_{0}(y) \right)
        \frac{ \| x - y \| }{\|y\|}
    \end{align}
    On the one hand,
    we compute the Jacobian  
    \begin{align}
        \Jacobian F(x) 
        \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
        \left( \sum_{i=1}^{n} \lambda_{i}(x) \right)
        \frac{x}{\|x\|} \left( \sum_{i=1}^{n} \nabla\lambda_{i}(x) \right)
    \end{align}

\end{document}

### 2024-08-15 main.tex
Update on Overleaf.
transformation

\begin{lemma}    
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Then $I$ is the union of $k$ different facets of $T$, 
    and their intersection is a simplex $S \in \calT$ of dimension $n-k$.
    Moreover, 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
\end{proof}

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let $M := |\patch_{\calT}(S)| \setminus T$. 
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \varphi : T \rightarrow M
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
        \quad 
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
\end{theorem}
\begin{proof}
\begin{itemize}
    \item 
    \todo{Choose hyperplane that puts T on one side}
    We use Lemma~\ref{lemma:oppositesubsimplex}
    \item 
    \todo{Align barycenter of opposite subsimplex with coordinate axis}
    \item 
    \todo{opposite simplex cast to disk}
    \item 
    \todo{roll out rest of sphere onto disk}
    \item 
    \todo{estimate reflection}
\end{itemize}
\end{proof}

>>>>

Stars around subsimplices can be turned into vertex stars after a subdivision, 
and the shape regularity can be controlled.

\begin{lemma}\label{lemma:stardivision}
    Let $\calT$ be an $n$-dimensional simplicial complex
    such that $\calT = \patch_{\calT}(S)$ for some $S \in \calT$.
    Let $z_S$ be the barycenter of $S$ 
    and let $\calT^{\star}$ be the simplicial complex obtained from barycentric subdivision of $S$.
    If $T^{\star} \in \calT^{\star}$ and $T \in \calT$ are both $n$-dimensional with $T^{\star} \subseteq T$,
    then $\vol(T^{\star}) = \vol(T) / n$.
\end{lemma}
\begin{proof}
    This is easy.
\end{proof}

\begin{lemma}    
    Suppose that an $n$-dimensional manifold triangulation $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots, T_{M}$.
    For $0 \leq m < M$, write 
    $$
        X_{m} := T_{0} \cup T_{1} \cup \dots \cup T_{m},
        \qquad 
        I_{m} := X_{m} \cap T_{m+1}.
    $$ 
    Whenever $I_{m}$ is the union of $k$ different facets of $T$, 
    then the intersection of those facets is a simplex $S \in \calT$ of dimension $n-k$ that satisfies 
    $$
        \patch_{X_{m+1}}(S) = \patch_{\calT}(S).
    $$
\end{lemma}
\begin{proof}
    We know $I_{m}$ is a submanifold of the boundary of $T$, and so it must be a collection of $k$ facets
    that constitute the local patch around some simplex $S$ of dimension $n-k$.
    To show that $\patch_{X_{m+1}}(S) = \patch_{\calT}(S)$, let us assume that $T \in \patch_{\calT}(S) \setminus \patch_{X_{m+1}}(S)$.
    By assumption, $S$ must be a boundary simplex of $X_{m+1}$. 
    \todo{Complete this here. The barycenter is contained in the interior of a boundary disk.}
\end{proof}

\begin{theorem}\label{theorem:starreflection}
    Let $\calT$ be an $n$-dimensional triangulation and let $S \in \calT$ be a simplex of dimension $k < n$.
    Let $T \in \patch_{\calT}(S)$ be of dimension $n$ and let 
    \begin{align*}
        M := |\patch_{\calT}(S)| \setminus T.
    \end{align*}
    There exists a bi-Lipschitz mapping
    \begin{align*}
        \varphi : T \rightarrow M
    \end{align*}
    satisfying
    \begin{align*}
        \Lip( \varphi,      T ) \leq \Cvier{n}{k} \diam(T),
        \quad 
        \Lip( \varphi^{-1}, M ) \leq \Cfive{n}{k} \diam(T),
    \end{align*}
    where $\Cvier{n}{k} \leq ...$ and $\Cfive{n}{k} \leq ...$
\end{theorem}
\begin{proof}
    Without loss of generality, the barycenter of $S$ is the origin. 
    We derive the estimate in several steps. 
    \begin{itemize}
        \item 
        Let $I := M \cap T$, which is the union of $k$ different faces of $T$, with $1 \leq k \leq n$.
        We let $J \subseteq \partial T$ be the union of the remaining $n+1-k$ faces of $T$.
        So $J$ is in the boundary of $|\calT|$ and is disjoint from $S$.
        The subsimplex $S' \subseteq T$ that is complementary to $S$.
        such that $J$ is the union of exactly those faces of $T$ that contain $S'$.

        \item 
        We construct a new triangulation that contains $T$ and that is a star around $S$.
        For that purpose, we let $z'_{S}$ be the midpoint of $S'$. 
        We define a triangulation $\calS$ by the barycentric refinement of $T$. 
        All $n$-simplices in $\calS$ contain $S$ and $z'_{S}$.

        We define another simplicial complex $\calS^c$ as follows:
        whenever $K \in \calS$ is an $n$-simplex, we replace the vertex $z_{S}'$ by new vertex opposite point $-z_{S}'$,
        giving us a simplex $K'$.

        We let $\calS'$ be the union of $\calS$ and $\calS^c$. 
        By construction, all these $n$-simplices contain $S$ as a subsimplex,
        and they are disjoint except for their proper subsimplices. 
        Hence $\calS'$ is indeed a triangulation. 
        Moreover, $S$ is an inner subsimplex of that triangulation. 
        In particular, $\calS'$ is its own star around $S$.

        In what follows, we also use $\calS''$, the simplicial complex obtained from $\calS'$ by barycentric subdivision of $S$.
        Then $\calS''$ is the local star around the barycenter $z_S$.

        \item 
        \todo{Reflect onto complement and estimate bi-Lipschitz constant}
        We introduce a new mapping $\Theta : |\calS| \rightarrow |\calS^c|$.

        \item 
        Consider any $n$-simplex $T$ with vertices $v_0, v_1, \dots, v_n$, where $v_0$ is the origin. 
        We let $A_T \in \bbR^{n \times n}$ be the matrix that maps the $i$-th unit vector to $v_i$.
        That matrix maps the reference simplex $\Delta^{n}$ onto $T$. 
        Then the mapping 
            F_T(x) 
            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x
        maps $T$ onto a ``simplex with a curved face'' inside the Euclidean unit ball. Its inverse is
            F_T^{-1}(x) 
            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x
        We analyze its Lipschitz properties.
        On the one hand, 
        we compute the Jacobian at any $x \in \mathring T$:
            \Jacobian F_T(x) 
            \frac{ \Id \|x\| - x \|x\|^{-1} x^t }{\|x\|^2} 
            \left( \vecone \cdot A^{-1} x \right)
            \frac{x}{\|x\|} \left( \vecone \cdot A^{-1} x \right)
        The Euclidean operator norm is 
            \| \Jacobian F_T(x) \| 
            2 \left| \vecone \cdot A^{-1} x \right|
            2 \sqrt{n} \cdot \sigma_{\max}(A^{-1}) 
        On the one hand, given $x, y \in T$, 
        where $\| y \|_{1} \leq \| x \|_{1}$ without loss of generality, we find 
            \left\| F_T(x) - F_T(y) \right\|_{2}
            \left\| 
                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
            \left\| 
                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } x - \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y
            \right\|_{2}
            \left\| 
                \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } y - \frac{ \| A^{-1} y \|_{1} }{ \|y\|_2 } y
            \right\|_{2}
            \frac{ \| A^{-1} x \|_{1} }{ \|x\|_2 } 
            \left\| 
                x - y
            \right\|_{2}
            \left| \|A^{-1} x\|_2 - \|A^{-1} y\|_2 \right|
            \left( \sqrt{n} + 1 \right) \sigma_{\max}(A^{-1}) 
            \left\| x - y \right\|_{2}
        On the other hand, given $x, y \in F_T(T)$, 
        where $\| A^{-1} y \|_{1} \leq \| A^{-1} x \|_{1}$ without loss of generality, we find 
            \left\| F_T^{-1}(x) - F_T^{-1}(y) \right\|_{2}
            \left\| 
                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
            \right\|_{2}
            \left\| 
                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } x - \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y
            \right\|_{2}
            \left\| 
                \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } y - \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} } y
            \right\|_{2}
            \frac{ \|x\|_2 }{ \| A^{-1} x \|_{1} } 
            \left\| 
                x - y
            \right\|_{2}
            \left| \|x\|_2 - \|y\|_2 \right|
            \frac{ \|y\|_2 }{ \| A^{-1} y \|_{1} }
            2 \sigma_{\min}(A^{-1})^{-1} 
            \left\| x - y \right\|_{2}
        By convexity of the range of $F_T(T)$, 
        we obtain a bound on the operator norm of the Jacobian of $F_{T}^{-1}$. 
        We recall that $\sigma_{\max}(A^{-1}) = \sigma_{\min}(A)^{-1}$ and $\sigma_{\min}(A^{-1})^{-1} = \sigma_{\max}(A)$.

        \item 
        Suppose that $S = \{v_0\}$ is a single vertex. 
        We construct a transformation from the vertex star around $S$ onto the Euclidean unit ball. 
        Without loss of generality, $S$ is at the origin. 
        For any $T \in \patch_{\calT}(S)$, we let $F_T$ be the transformation. 
        We define $F$ over $|\patch_{\calT}(S)|$ piecewise. 
        \todo{Complete}

        \item 
        \todo{Combine all this to get the final transformation.}

%         \item 
%         Let $\calU$ be the simplicial complex of dimension $n-1$ that contains precisely those facets of $T$ that do not contain $S$.
%         We write $Y := F( |\calU| )$. 
%         \todo{Shape of the outer patch $Y$, star-shaped geometry}
%         
%         \item 
%         We let $\sphere{n}_{\star} := \sphere{n} \setminus \{e_{n+1}\} \subseteq \bbR^{n+1}$ be the unit sphere without the North pole. 
%         Suppose that $\bar x \in \sphere{n}$ is a point on the unit sphere and $\bar x \neq e_{n+1}$. 
%         We define its stereographic projection as 
%         \begin{align}
%             \pi( \bar x ) 
%             = 
%             \sum_{i=1}^{n} \frac{x_i}{1 - x_{n+1}} e_{i}
%             .
%         \end{align}
%         This is a mapping $\pi : \sphere{n}_{\star} \rightarrow \bbR^{n}$. 
%         Its inverse is defined as follows: given $y \in \bbR^{n}$, we have 
%         \begin{align}
%             \pi^{-1}( y )
%             = 
%             \sum_{i=1}^{n} \frac{2 y_i}{1 + \| y \|^2} e_{i}
%             +
%             \frac{1 - \| y \|^2}{1 + \| y \|^2} e_{n+1}
%             .
%         \end{align}
%         \item 
%         Mirroring the unit sphere along the equator is expressed in stereographic coordinates by the involution 
%         \begin{align}
%             \mu : \bbR^{n} \rightarrow \bbR^{n},
%             \qquad 
%             y \mapsto \frac{y}{\| y \|}.
%         \end{align}
%         \item 
%         \begin{align}
%             G(y) := \| y \| \cdot \phi\left( \frac{y}{\|y\|} \right)^{-1} \frac{y}{\|y\|}
%         \end{align}
%         \item 
%         We combine these mappings:
%         \begin{align}
%             Q : \sphere{n} \rightarrow \sphere{n}, \qquad x \mapsto \pi^{-1} G^{-1} \mu G \pi(x)
%         \end{align}
%         We want to analyze its Lipschitz properties. \todo{Stuff}
%         \item
%         We have constructed a bi-Lipschitz mapping from the Euclidean unit sphere into itself.
%         We use the following result~\cite[Theorem~3]{alestalo2018radial}:
%         if $f : \sphere{n} \rightarrow \sphere{n}$ is any $L$-Lipschitz mapping from the Euclidean unit sphere into itself, 
%         then the radial extension $f : \ball{n} \rightarrow \ball{n}$ is an $L$-Lipschitz mapping from the Euclidean unit ball into itself.
%         Consequently, \todo{write out}
%         \item 
%         In total, we thus have 
%         \begin{align}
%             Q' := F^{-1} \pi^{-1} G^{-1} \mu G \pi F
%             .
        \end{align}
    \end{itemize}
\end{proof}

% Please cite the original version:
% Alestalo, P., & Trotsenko, D. A. (2018). Radial extensions of bilipschitz maps between unit spheres. Siberian
% Electronic Mathematical Reports, 15, 839-843. https://doi.org/10.17377/semi.2018.15.071
% Theorem 3: radial extension of bi lipschitz between unit spheres, with same constant
